%This document demonstrates proper use of REV\TeX~4 (and
%\LaTeXe) in mansucripts prepared for submission to APS
%journals. Further information can be found in the REV\TeX~4
%documentation included in the distribution or available at
%\url{http://publish.aps.org/revtex4/}. 
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.0 .
% If you compile your tex files on the Physics
% server, everything is already set up for you.
%

% Choose the format that suits your purposes.  The top line gives the
% two column (twocolumn) format that one sees in printed journals.  The
% second line refers to a one column double spaced format (preprint) that
% is useful during editing.  Use the "%" symbol to edit out the line
% you do not want to use.

%\documentclass[draft, twocolumn,showpacs,preprintnumbers,amsmath,amssymb]{revtex4}
\documentclass[syntaxonly, twocolumn,preprintnumbers,amsmath,amssymb]{revtex4}
%\documentclass[twocolumn,preprintnumbers,amsmath,amssymb]{revtex4}

%\documentclass[preprint,showpacs,preprintnumbers,amsmath,amssymb]{revtex4}
% Additional packages needed for graphics, alignment and math fonts.

\usepackage{graphicx}% Include figure files in eps format.
\usepackage{dcolumn}% Align table columns on decimal point.
\usepackage{bm}% bold math.

\usepackage{ifdraft}
\usepackage{syntonly}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{glossaries}
\usepackage{IEEEtrantools}
\usepackage{blindtext}
\loadglsentries{acronyms.tex}

\input{generated_tex/acronym_macros.tex}
\newcommand{\vm}{\vec{M}}
\newcommand{\cc}{{\bf C}}
\newcommand{\erf}{\text{erf}}


% The \begin{document} command set the start of the RevTeX commands.

\begin{document}

\title{Identification and Quantification of Diffusion MRI Biomarkers to Study Spinal Cord Injury}

\author{Marcus Lee}
\email{marcus99@student.ubc.ca}
\affiliation{Department of Physics and Astronomy, University of British Columbia \\
             6224 Agricultural Road, Vancouver, British Columbia, Canada, V6T 1Z1}

\date{\today}

\begin{abstract}
\ifdraft{
Provide a brief summary of the proposal here. This  should be a concise  
statement of what will be accomplished, the methods that will be used, and the potential significance. Many of you have already sent me a description of the project that can be put here with some  touching up. I will only  accept LATEX complied files in pdf format. They must be emailed to me a few days  before the oral presentations.  Make sure your supervisor has a chance to read it over before you hand it in. }
{
    \input{abstract.tex}
}

\end{abstract}

\maketitle

% The first section of the paper.

\section{Motivation}
\ifdraft{
In this section introduce the subject of the proposal and  provide all the necessary background information that will be needed for a {\bf non-expert} to understand.  This  should involve reading at least 5-10 journal articles some of which your supervisor will likely provide and others you will need to look up. These should all be listed in the bibliography. 
Items in the bibliography can be referenced  as follows. The text inside the curly brackets are
used to label the references. Numbers appear automatically in the compiled
text.

Most importantly you must provide  the scientific motivation for why this project should be carried out and what scientific impact it could have if  it were completely successful. Any research project requires a substantial  investment of resources (money for equipment, use of common facilities, computer time for calculations/data analysis, the countless hours spent by you and your supervisor etc.) You must convince  the reader/reviewer that the project and the potential outcome is worth this investment. Imagine that only a fraction of the  proposals submitted will be approved. If yours is not approved then you must rework the proposal or find another project for which the scientific justification is stronger.  This is typical of the competitive  environment one is often faced with in research. There is always  a demand for  resources and/or access to facilities which exceeds the availability.  Only the best projects get funded or receive time on a facility (e.g. telescope or accelerator). It is  your responsibility to make the case that your proposal  should be  approved. In this case I am the reviewer who decides if you get approval.}
{
    \input{motivation.tex}
}

\section{Theory}
\ifdraft{

In this section provide details on the theory  needed to clarify the physics/astophysics behind the proposal. If you are building an ESR spectrometer you would need to explain the Zeeman interaction of an electron in a magnetic field. Use diagrams wherever possible. These can be reused or revised
later for subsequent oral presentations and the thesis. Spend the time now to make up some good ones.
Important  points are: (1) they must be  legible. (2) all axis properly labelled with units  etc. (3)any photos sketches should have a scale built in.   (4) Data point and uncertainties  must  be clearly visible.  

}{
    \input{theory.tex}
}

\input{calculation.tex}


\section{Resources List}
\ifdraft{
Provide a detailed list of all the resources you will need. e.g. any instruments, equipment materials  and where it will come from. If it is going be bought then indicate the delivery time. Indicate what computing needs for the project and where they will come from.}
{
    \input{resources.tex}
}

\section{Planned Schedule}
\input{schedule.tex}

\section{Acknowledgements}
\input{acknowledgement.tex}

% Finally, make the bibliography
\ifdraft{
    % pass
}{
\bibliography{references.bib}
}
    

\end{document}
%
% ****** End of file  ******